Cost of Living in Toronto

### 2024-09-22 paper/paper.qmd
fixed a launch error in paper.qmd

library(palmerpenguins)
library(opendatatoronto)
library(tidyverse)
library(dplyr)
library(sf)
```

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

\newpage

>>>>

# RUN THIS IN THE TERMINAL IF THERE'S AN ERROR IN EXPORTING TO PDF
# Source: https://stackoverflow.com/questions/75906430/why-cant-i-render-any-quarto-documents-into-pdfs
# quarto install tool tinytex

library(opendatatoronto)
library(tidyverse)
library(dplyr)
library(sf)

# Read the 2 cleaned CSV files
analysis_data = read_csv('data/cleaned_data/cleaned_data.csv')
analysis_data_inverted = read_csv('data/cleaned_data/cleaned_data_inverted.csv')

analysis_data
analysis_data_inverted

```

@@

testing testing
